Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-06-28 Documents/Paper/ms.tex
Don't go to sampling so soon

Here we have assumed the priors for $N$ and $\hyperparams$ are independent, and
the interim prior for $\{\xx_i\}$ is iid and does not depend on $N$.
Given data $\mathcal{D}$, we usually want to generate samples from the
posterior distribution given by:
\begin{eqnarray}
p(N, \hyperparams, \{\xx_i\} | \mathcal{D}) \propto
p(N, \hyperparams, \{\xx_i\})
p(\mathcal{D} | N, \hyperparams, \{\xx_i\})\label{eq:bayes}
\end{eqnarray}
The marginal likelihood, or evidence, is also an important quantity, and is
the normalisation constant of the posterior given in Equation~\ref{eq:bayes}:
\begin{eqnarray}
\mathcal{Z} &=& p(\mathcal{D})\\
&=& \sum_{i=0}^{N_{\rm max}} \int
p(N, \hyperparams, \{\xx_i\})p(\mathcal{D} | N, \hyperparams, \{\xx_i\})
\, d^N \xx_i \, d\hyperparams \label{eq:evidence}
\end{eqnarray}

>>>>

Here we have assumed the priors for $N$ and $\hyperparams$ are independent, and
the interim prior for $\{\xx_i\}$ is iid and does not depend on $N$.
Given data $\mathcal{D}$, we usually want to calculate properties of the
posterior distribution given by:
\begin{eqnarray}
p(N, \hyperparams, \{\xx_i\} | \mathcal{D}) \propto
p(N, \hyperparams, \{\xx_i\})
p(\mathcal{D} | N, \hyperparams, \{\xx_i\})\label{eq:bayes}
\end{eqnarray}
The general method used to calculate properties of the posterior distribution
is to generate samples from it using Markov Chain Monte Carlo (MCMC).

The marginal likelihood, or evidence, is also an important quantity, and is
the normalisation constant of the posterior given in Equation~\ref{eq:bayes}:
\begin{eqnarray}
\mathcal{Z} &=& p(\mathcal{D})\\
&=& \sum_{i=0}^{N_{\rm max}} \int
p(N, \hyperparams, \{\xx_i\})p(\mathcal{D} | N, \hyperparams, \{\xx_i\})
\, d^N \xx_i \, d\hyperparams \label{eq:evidence}
\end{eqnarray}
